Towards a Mechanized Proof of Noninterference

### 2013-12-19 paper/paper.tex
more copyediting

While programming in this language becomes much more burdensome, we
feel that the removal of these features does not fundamentally 
change the problem of proving
noninterference.  Mechanizing a proof of noninterference for a
language closer to \origLang would require simply adding mechanized proofs
for the additional cases where appropriate.

We also decided to replace the
\textsf{case} construct from \origLang with an \textsf{if} construct, which
evaluates the first expression if the test evaluates to 1 and evaluates to the
second expression otherwise.

>>>>

While programming in this language becomes much more burdensome, we
feel that the removal of these features does not fundamentally 
change the problem of proving
noninterference.  Mechanizing a proof of noninterference for a
language closer to \origLang would require adding mechanized proofs
for the additional cases where appropriate.

We also decided to replace the
\textsf{case} construct from \origLang with an \textsf{if} construct, which
evaluates the first expression if the test evaluates to 1 and evaluates to the
second expression otherwise.  This simplifies our proof structure by eliminating
one case of capture-avoiding substitution.
